### 2023-01-21 manuscript.Rmd
Make `read_log` code and comments clearer

  # Read the file
  read_tsv(
    log_file,
    col_types = cols(),
    locale = locale(encoding = "latin1")
  ) %>%
    # Recode some columns
    transmute(

      # Phase of the experiment
      phase = factor(Wdh,
        levels = c(211, 212, 213),
        labels = c("Pre-insight", "Insight", "Post-insight")
      ),

      # Keyword conditions
      keywords = factor(Bed,
        levels = c("richtig", "falsch"),
        labels = c("Match", "Non-match")
      ),

      # Behavioral responses
      # 201: "I know what this is or have a strong assumption"  -> Recode as 4
      # 202: "I have an assumption what this is"                -> Recode as 3
      # 203: "I have rather no assumption what this is"         -> Recode as 2
      # 204: "I don't know what this is and have no assumption" -> Recode as 1
      response = 5 - (Tastencode - 200),

@@

      # Item IDs
      item_id = factor(StimID)
    ) %>%
    # Remove filler items
    drop_na(keywords) -> log

@@

      # Exclude: Positive response *before* any info was presented
      Exclude_known = item_id[phase == "Pre-insight" & response == 4]
    )
  })

>>>>

  # Read the file
  log <- read_tsv(
    log_file,
    col_types = cols(),
    locale = locale(encoding = "latin1"),
    progress = FALSE
  ) %>%
    # Recode some columns
    transmute(

      # Phase of the experiment
      phase = factor(
        Wdh,
        levels = c(211, 212, 213),
        labels = c("Pre-insight", "Insight", "Post-insight")
      ),

      # Unfamiliar versus familiar objects
      familiarity = factor(
        bek_unbek,
        levels = c("bekannt", "unbekannt"),
        labels = c("familiar", "unfamiliar")
      ),

      # Matching versus non-matching keywords for unfamiliar objects
      keywords = factor(
        Bed,
        levels = c("richtig", "falsch"),
        labels = c("Match", "Non-match")
      ),

      # Behavioral responses
      # Button code 201: "I know what this is or have a strong assumption"
      # Button code 202: "I have an assumption what this is"
      # Button code 203: "I have rather no assumption what this is"
      # Button code 204: "I don't know what this is and have no assumption"
      # Button code 0: Technical glitch
      response = recode(
        Tastencode,
        `201` = 4, `202` = 3, `203` = 2, `204` = 1, `0` = NA_real_
      ),

@@

      # Item IDs
      item_id = factor(StimID)
    ) %>%
    # Remove filler items
    filter(familiarity == "unfamiliar")

@@

      # Exclude: Positive response *before* any info was presented
      Exclude_known = item_id[phase == "Pre-insight" & response == 4],

      # Exclude: Technical glitch
      Exclude_glitch = item_id[phase == "Insight" & is.na(response)]
    )
  })
